---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figure/",
  fig.height = 1
)
```

# Ari Aster Palettes

Color palettes inspired by the films of Ari Aster. Each palette is drawn from the distinct visual language of *Hereditary*, *Midsommar*, *Beau Is Afraid*, and *Eddington*.

This package is built upon the structure and framework of the [wesanderson](https://github.com/karthik/wesanderson) package 
(Karthik Ram, Hadley Wickham), adapted with original palettes.

## Installation

```r
# Development version
devtools::install_github("zhorve/aripalettes")
```

## Usage

```{r palettes_dummy}
library("ariaster")

# See all palettes
names(ari_palettes)
```

## Palettes

### Hereditary (2018)

```{r hereditary, fig.height = 1}
ari_palette("Hereditary1")
ari_palette("Hereditary2")
ari_palette("Hereditary3")
ari_palette("Hereditary4")
```

### Midsommar (2019)

```{r midsommar, fig.height = 1}
ari_palette("Midsommar1")
ari_palette("Midsommar2")
ari_palette("Midsommar3")
ari_palette("Midsommar4")
```

### Beau Is Afraid (2023)

```{r beau, fig.height = 1}
ari_palette("Beau1")
ari_palette("Beau2")
ari_palette("Beau3")
ari_palette("BeauMonster")
```

### Eddington (2025)

```{r eddington, fig.height = 1}
ari_palette("Eddington1")
ari_palette("Eddington2")
ari_palette("Eddington3")
```

## Continuous palettes

Any palette can be interpolated to generate as many colors as you need:

```{r volcano, fig.height = 3}
pal <- ari_palette("Beau1", 21, type = "continuous")
image(volcano, col = pal)
```

```{r volcano2, fig.height = 3}
pal <- ari_palette("Eddington1", 21, type = "continuous")
image(volcano, col = pal)
```

## Palette previews

The `test_palette()` function shows a palette across four chart types — useful for checking how colors hold up in real use.

```{r test_hereditary2, fig.height = 6}
test_palette("Midsommar1")
```

```{r test_midsommar1, fig.height = 6}
test_palette("Eddington3")
```

```{r test_eddington1, fig.height = 6}
test_palette("Beau3")
```
